---
title: "日本語"
output:
  beamer_presentation:
    latex_engine: xelatex
  ioslides_presentation: default
  slidy_presentation: default
header-includes:
- \usepackage{xltxtra}
- \usepackage{zxjatype}
- \usepackage[ipa]{zxjafont}
- \uselanguage{japanese}
- \languagepath{japanese}
- \deftranslation[to=japanese]{Theorem}{定理}
- \deftranslation[to=japanese]{Lemma}{補題}
- \deftranslation[to=japanese]{Example}{例}
- \deftranslation[to=japanese]{Examples}{例}
- \deftranslation[to=japanese]{Definition}{定義}
- \deftranslation[to=japanese]{Definitions}{定義}
- \deftranslation[to=japanese]{Problem}{問題}
- \deftranslation[to=japanese]{Solution}{解}
- \deftranslation[to=japanese]{Fact}{事実}
- \deftranslation[to=japanese]{Proof}{証明}
- \def\proofname{証明}
---

## R Markdown
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```
	
## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

